\begin{thebibliography}{5}
    \footnotesize
    \bibitem{officialstats}
        \textit{YouTube Statistics}
        [Online].
        Available:
        https://www.youtube.com/yt/press/statistics.html
        [Accessed: 2015-11-01].
    \bibitem{dagensmediastats}
        K. Djerf.
        (2014-11-12).
        \textit{300 timmar film laddas upp p\aa\  Youtube – i minuten}
        [Online].
        Available:
        http://www.dagensmedia.se/nyheter/article3863831.ece
        [Accessed: 2015-11-01].
    \bibitem{reelseostats}
        M.R. Robertson.
        (2014-11-21).
        \textit{300+ HOURS OF VIDEO UPLOADED TO YOUTUBE EVERY MINUTE}
        [Online].
        Available:
        http://www.reelseo.com/youtube-300-hours/
        [Accessed: 2015-11-01].
    \bibitem{iso-dash-2014}
        \textit{Information Technology - Dynamic adaptive streaming over HTTP (DASH)},
        ISO/IEC 23009-1, 2014.
    \bibitem{youtube-dl:youtube.py}
        P. Hagemeister et al.
        \textit{youtube.py}
        [Online].
        Available:
        https://github.com/rg3/youtube-dl/blob/master/youtube\_dl/extractor/youtube.py
        [Accessed: 2015-11-01, git commit 5c43afd].
    \bibitem{youtube-dl}
        P. Hagemeister et al.
        \textit{youtube-dl}
        [Online].
        Available:
        https://github.com/rg3/youtube-dl
        [Accessed: 2015-11-01].
    \bibitem{conclusion:gdataissue}
        \textit{Google Code server-side issues and feature requests for YouTube Data API v3}
        [Online].
        Available:
        https://code.google.com/p/gdata-issues/issues/list?q=label:API-YouTube
        [Accessed 2015-11-01].
    \bibitem{Google I/O 2013}
        M. Ward and S. Robinson.
        (2013-05-18).
        \textit{Google I/O 2013 - Adaptive Streaming for You and YouTube}
        [Online].
        Available:
        https://www.youtube.com/watch?v=UklDSMG9ffU
        [Accessed: 2015-11-02].
    \bibitem{adobe-http-dynamic-streaming}
        \textit{HTTP Dynamic Streaming}
        [Online].
        Available:
        http://www.adobe.com/products/hds-dynamic-streaming.html
        [Accessed: 2015-11-02].
    \bibitem{apple-http-streaming}
        \textit{Apple HTTP Live Streaming}
        [Online].
        Available:
        https://developer.apple.com/streaming/
        [Accessed: 2015-11-02].
    \bibitem{microsoft-smooth-streaming}
        \textit{Microsoft Smooth Streaming}
        [Online].
        Available:
        http://www.iis.net/downloads/microsoft/smooth-streaming
        [Accessed: 2015-11-02].
    \bibitem{dashing-youtube}
        D.K. Krishnappa et al.
        \textit{DASHing YouTube: An analysis of using DASH in YouTube video service}
        [Online].
        Available:
        http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6761273
        [Accessed: 2015-11-02].
    \bibitem{rfc6381}
        R. Gellens et al.
        \textit{The 'Codecs' and 'Profiles' Parameters for "Bucket" Media Types}
        [Online].
        Available:
        https://tools.ietf.org/html/rfc6381
        [Accessed: 2015-11-02].
    \bibitem{youtube-recommendation-system}
        J. Davidson et al.
        \textit{The YouTube Video Recommendation System}
        [Online].
        Available:
        http://www.inf.unibz.it/~ricci/ISR/papers/p293-davidson.pdf
        [Accessed: 2015-11-02].
    \bibitem{stockhammer-dash}
        T. Stockhammer,
        "Dynamic Adaptive Streaming over HTTP – Standards and Design Principles",
        in International Multimedia Conference,
        San Jose, CA,
        2011.
    \bibitem{youtube-api}
        \textit{API Reference}
        [Online].
        Available:
        https://developers.google.com/youtube/v3/docs
        [Accessed: 2015-11-02].
\end{thebibliography}
